Python as a machine learning language: experiences from the scikit-learn project

### 2013-06-15 paper.tex
Indentation.
wordings in the conclusions

Although it is coming close to a 1.0 release, \sklearn is by no means finished.
At the time, it does not support many classical machine learning tasks. Among
others, missing features include neural networks, ensemble meta-estimators for
bagging or subsampling strategies, or missing value completion algorithms
provided as transformers.  However, topics like structured prediction or
reinforcement learning are considered off-topic for the project, since they
would require quite different data representations and API.

>>>>

Although it is coming close to a 1.0 release, \sklearn is by no means finished.
At the time, it does not support many classical machine learning tasks. Among
others, missing features include neural networks, ensemble meta-estimators for
bagging or subsampling strategies, or missing value completion algorithms.
Topics like structured prediction or reinforcement learning are however
considered off-topic for the project, since they would require quite different
data representations and API.
